Reproduce anaylses of Beninca et al (2008)

### 2016-02-12 code/report.Rmd
update rmarkdown report
small fixes

Next calculate the Lyapunov exponents, noting that 6 or 7 points were used in the regressions in the Nature report
```{r}
diverg$Difference[is.na(diverg$Difference)] <- 0
diverg$Difference[is.infinite(diverg$Difference)] <- 0
diverg.short <- filter(diverg, days<24) ## 24 is about 6 steps, after initial gap
LEs <- group_by(diverg.short, Species) %>%
  summarise(le=coef(lm(Difference[1:6] ~ days[1:6]))[2])
#pval=summary(lm(Difference[1:6] ~ days[1:6]))$coefficients[2,4])
```

@@

## don't run this as it takes a while
LE <- Get_GLE_Beninca(X)
save(LE, file="~/Desktop/GLE_estimate.Rdata")

>>>>

Next calculate the Lyapunov exponents, noting that 6 or 7 points were used in the regressions in the Nature report
```{r}
#diverg$Difference[is.na(diverg$Difference)] <- 0
diverg$Difference[is.infinite(diverg$Difference)] <- NA
diverg.short <- filter(diverg, days<24) ## 24 is about 6 steps, after initial gap
LEs <- group_by(diverg.short, Species) %>%
  summarise(le=coef(lm(Difference[1:6] ~ days[1:6]))[2])
#pval=summary(lm(Difference[1:6] ~ days[1:6]))$coefficients[2,4])
```

@@

## don't run this unless you have some time (it takes a while)
LE <- Get_GLE_Beninca(X)
save(LE, file="~/Desktop/GLE_estimate.Rdata")
